---
title: "Informative Visualization using Iris Data"
description: |
  Data visualization is a crucial step in data science and data understanding. in this short article, I will demonstrate how powerful visualization can be in answersing some critical questions. 
  
  (---not complete yet)
author:
  - name: Zakarie Hashi, MS In Applied Statistics 
    url: https://zakarie.github.io/myBlog/
    affiliation: Westtern Michigan University
    affiliation_url: https://wmich.edu
date: 08-28-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = F,
  message = F,
  comment = "##",
  R.options = list(width = 60)
)
```


## Loading Required libraries
These are the libraries we will need. R libraries do a lot of functionalities. some help us ploting and some to do data manipulation. 

```{r}
library(devtools)
#devtools::install_github("ggobi/ggally")
#devtools::install_github("hrbrmstr/hrbrthemes")
# devtools::install_github("hrbrmstr/pluralize")
# devtools::install_github("kassambara/ggpubr")
library(tidyverse)
library(grid)
library(rvest)
library(stringi)
library(hrbrthemes)
library(ggthemes)
library(ggpubr)
```


## 1 Nillion Question.

Data science is all about solving a problem. for demonstration purposes, let us say your manager is interested in the following question **How features like sepal length, sepal width  affect species ?**. He/she asked you to do analysis and come up some solutions. 

Now, its your time as a data scientist to dive in and roll up your sleeves and show off what you got ( your skills).

What is common in bussiness setting or in data science teams is that, no manager will come up the right hypothesis for you or what analytical methods to use, they give you some testtable questions and you are the one who need to refrom these questions into hypothesis setting. Do not worrry if it did not click it now, we will do this together. 

Secondly, When you are given clear question to answer, avoid follwing the data but rather use the data to see if it validates the testable hypothesis you have or not then you are done. 

Typical data scientist spend 80% of their time on exploring the data and cleaning it (EDA) and 20% modeling stage. 

Explanatory analysis provides powerful insights on releaving relationship between features and the outcome you are interested which helps you later ways to model the data but there is a very crucial step that successful data scientists use which many data scientist lack which is **design thinking**. 50% of the EDA process should be design thinking. good design thinking leads to powerful EDA insights. 

Design thinking is defined as 

```{r}
iris.raw <- iris
head(iris, n=5)
```

